\documentclass[12pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage[top=2cm, bottom=4.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage{lastpage}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  linkbordercolor={0 0 1}
}
 
\definecolor{javared}{rgb}{0.6,0,0} % for strings
\definecolor{javagreen}{rgb}{0.25,0.5,0.35} % comments
\definecolor{javapurple}{rgb}{0.5,0,0.35} % keywords
\definecolor{javadocblue}{rgb}{0.25,0.35,0.75} % javadoc

\lstset{
    language=Java,
    basicstyle=\ttfamily,
    keywordstyle=\color{javapurple}\bfseries,
    stringstyle=\color{javared},
    commentstyle=\color{javagreen},
    morecomment=[s][\color{javadocblue}]{/**}{*/},
    numbers=left,
    numberstyle=\tiny\color{black},
    stepnumber=1,
    numbersep=10pt,
    tabsize=4,
    showspaces=false,
    showstringspaces=false
}

\renewcommand{\lstlistingname}{Snippet}

\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.05in}

% Edit these as appropriate
\newcommand\course{ASRR Tech Training}
\newcommand\hwnumber{2}

\pagestyle{fancyplain}
\headheight 35pt
 
\chead{\textbf{\Large Module \hwnumber}}
\rhead{\course}
\lfoot{}
\cfoot{}
\rfoot{\small\thepage}
\headsep 1.5em

\begin{document}

\section*{\hwnumber. Strings}
Note: all your methods should be \lstinline{public static} in this module \\
Resources:
\begin{description}
    \item \href{http://tutorials.jenkov.com/java/strings.html}{Strings}
\end{description}


Problems
\begin{enumerate}
\item
Write a method that takes two strings as its input and returns the concatenated string as its output.

\item
Write a method that takes a string as its input and returns the last character of the string as its output.

\item
Write a method that takes a string as its input and returns whether the string is equal to "yes".

\item
Write a method that takes a string as its input and returns whether the string contains the word "yes" as its output.
The input should be case insensitive.

\item
Write a method that takes a string as its input. The method should replace every "yes" in the string with a "no".
It should then return the modified string.

\item
Write a method that takes a string as its input and returns whether the string starts 
with "the" and ends with "end" as its output.

\item
Write a method that takes a string as its input and returns the last 5 characters of the string as its output.

\item
Write a method that takes a string as its input and returns the first word of a string.
Hint: use \lstinline{String#indexOf} and \lstinline{String#substring}.
\begin{description}
    \item Example behavior:
    \item   
     \begin{tabular}{@{}rl@{}}
      Input: & "Hello world" \\
      Output: & "Hello"
     \end{tabular}
\end{description}

\item
Write a method that takes a string as its input and returns the 
following string "the color 'red' is red" for any given color (replace red with the input string).

\item
Write a method that takes a string as its input. The method should convert the input string to uppercase.
It should then return the modified string.

\end{enumerate}



\end{document}
