\documentclass[12pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage[top=2cm, bottom=4.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage{lastpage}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{tabularx}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  linkbordercolor={0 0 1}
}
 
\definecolor{javared}{rgb}{0.6,0,0} % for strings
\definecolor{javagreen}{rgb}{0.25,0.5,0.35} % comments
\definecolor{javapurple}{rgb}{0.5,0,0.35} % keywords
\definecolor{javadocblue}{rgb}{0.25,0.35,0.75} % javadoc

\lstset{
    language=Java,
    basicstyle=\ttfamily,
    keywordstyle=\color{javapurple}\bfseries,
    stringstyle=\color{javared},
    commentstyle=\color{javagreen},
    morecomment=[s][\color{javadocblue}]{/**}{*/},
    numbers=left,
    numberstyle=\tiny\color{black},
    stepnumber=1,
    numbersep=10pt,
    tabsize=4,
    showspaces=false,
    showstringspaces=false
}

\renewcommand{\lstlistingname}{Snippet}

\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.05in}

% Edit these as appropriate
\newcommand\course{ASRR Tech Training}
\newcommand\hwnumber{6}

\pagestyle{fancyplain}
\headheight 35pt
 
\chead{\textbf{\Large Module \hwnumber}}
\rhead{\course}
\lfoot{}
\cfoot{}
\rfoot{\small\thepage}
\headsep 1.5em

\begin{document}

\section*{\hwnumber. Classes: methods and the static keyword}
Note: class member methods should NOT be \lstinline{static} in this module \\
Resources:
\begin{description}
    \item \href{https://www.w3schools.com/java/java_class_methods.asp}{Classes: methods}
    \item \href{https://www.baeldung.com/java-static}{Classes: the static keyword}
\end{description}


Problems
\begin{enumerate}
\item
Create a class named "Vector" It should have the following attributes: x, y and z.
\begin{enumerate}
\item
Create a method in the class that prints the values of x, y and z.

\item
Create a method in the class that calculates the length of the vector.

\item
Create a method in the class that normalizes the attributes of the vector. It should use the
previous method in the calculation.

\item
Create a method in the class that adds two vectors together. It should return the sum of the two vectors as a new vector.
This method should NOT be \lstinline[]$static$ and it should only have ONE parameter.
\end{enumerate}

\item
What does the code in the following snippet do? And why does it lead to this behavior?
\begin{lstlisting}
public class Person {

    public int age;

    public void setAge(int newAge) {
        age = newAge;
    }

}

public class Main {

    public static void main(String[] args) {
        Person.setAge(3);
    }

}
\end{lstlisting}
\newpage

\item
What does the code in the following snippet do? And why does it lead to this behavior?
\begin{lstlisting}
public class Person {

    public int personCount = 0;

    public static void registerPerson() {
        personCount++;
    }

}

public class Main {

    public static void main(String[] args) {
        Person.registerPerson();
    }

}
\end{lstlisting}

\item
What does the code in the following snippet do? And why does it lead to this behavior?
\begin{lstlisting}
public class Car {
    public static int carCount = 0;

    public static Car produce() {
        carCount++;
        Car car = new Car();
        return car;
    }
}

public class Main {

    public static void main(String[] args) {
        Car.produce();
        Car.produce();
        Car.produce();
    }
    
}
\end{lstlisting}

\item
What are the effects of the static keyword?

\end{enumerate}

\end{document}
