\documentclass[12pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage[top=2cm, bottom=4.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage{lastpage}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{tabularx}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  linkbordercolor={0 0 1}
}
 
\definecolor{javared}{rgb}{0.6,0,0} % for strings
\definecolor{javagreen}{rgb}{0.25,0.5,0.35} % comments
\definecolor{javapurple}{rgb}{0.5,0,0.35} % keywords
\definecolor{javadocblue}{rgb}{0.25,0.35,0.75} % javadoc

\lstset{
    language=Java,
    basicstyle=\ttfamily,
    keywordstyle=\color{javapurple}\bfseries,
    stringstyle=\color{javared},
    commentstyle=\color{javagreen},
    morecomment=[s][\color{javadocblue}]{/**}{*/},
    numbers=left,
    numberstyle=\tiny\color{black},
    stepnumber=1,
    numbersep=10pt,
    tabsize=4,
    showspaces=false,
    showstringspaces=false
}

\renewcommand{\lstlistingname}{Snippet}

\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.05in}

% Edit these as appropriate
\newcommand\course{ASRR Tech Training}
\newcommand\hwnumber{7}

\pagestyle{fancyplain}
\headheight 35pt
 
\chead{\textbf{\Large Module \hwnumber}}
\rhead{\course}
\lfoot{}
\cfoot{}
\rfoot{\small\thepage}
\headsep 1.5em

\begin{document}

\section*{\hwnumber. Classes: constructors and the this keyword}
Resources:
\begin{description}
    \item \href{https://www.w3schools.com/java/java_constructors.asp}{Classes: constructors}
    \item \href{https://www.baeldung.com/java-this}{Classes: the this keyword}
\end{description}


Problems
\begin{enumerate}
\item
Create a class named "Point" It should have the following attributes: x and y.
\begin{enumerate}
\item
Create a constructor with parameters x and y (the parameters MUST have these names) that initializes the fields in this class.

\item
Create an overloaded constructor without any parameters in this class.
The fields x and y should be initialized with the value 0.

\item
Create a method named "print" that prints the values of the fields x and y.

\item
Create a new Point instance with your constructor in your main method. Try to create objects with both
constructors and then use the print method to print their coordinates.

\end{enumerate}

\item
What does the code in the following snippet do? And why does it lead to this behavior?
\begin{lstlisting}
public class Person {

    public int age = 0;

    public static void updateAge(int age) {
        this.age = age;
    }

}

public class Main {

    public static void main(String[] args) {
        Person.updateAge(3);
    }

}
\end{lstlisting}

\newpage

\item
To which monkey does "this" refer to in the compare method (explain why)?
\begin{lstlisting}
public class Monkey {

    private String name;

    public Monkey(String name) {
        this.name = name;
    }

    public boolean compare(Monkey o) {
        return this.name.equals(o.name);
    }

}

public class Main {

    public static void main(String[] args) {
        Monkey a = new Monkey("a");
        Monkey b = new Monkey("b");
        a.equals(b);
    }

}
\end{lstlisting}

\item
What does the this keyword do?

\end{enumerate}

\end{document}
